---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# Homework6

<!-- badges: start -->
[![R-CMD-check](https://github.com/nikhildevireddy/SDS375_Homework6/actions/workflows/R-CMD-check.yml/badge.svg)](https://github.com/nikhildevireddy/SDS375_Homework6/actions/workflows/R-CMD-check.yml)
<!-- badges: end -->

 `Homework6` offers an S4 sparse_numeric class for compactly storing sparse numeric vectors plus fast operations—addition, subtraction, elementwise products, cross-products, mean, norm, and standardization. It’s designed for zero-heavy vectors so you keep only the nonzero entries while still working with them efficiently.

## Installation

You can install the development version of **Homework6** from GitHub

```{r setup, include = FALSE}
devtools::load_all(".")
```

```r
# install.packages("pak")
pak::pak("nikhildevireddy/Homework6")
```

## Examples

How the package is used to construct sparse vectors and execute arithmetic operations:

```{r}
library(Homework6)

# Create two numeric vectors
x <- c(0, 5, 0, 3)
y <- c(2, 0, 0, 7)

# Convert to sparse_numeric
sx <- as(x, "sparse_numeric")
sy <- as(y, "sparse_numeric")

# Addition
sparse_add(sx, sy)

# Elementwise multiplication
sparse_mult(sx, sy)

# Compute the norm
norm(sx)

# Standardize the vector
standardize(sx)
```

## Package Methods

- A compact S4 representation of sparse numeric vectors  
- Vectorized arithmetic: `+`, `-`, `*`  
- Generic functions:
  - `sparse_add()`
  - `sparse_sub()`
  - `sparse_mult()`
  - `sparse_crossprod()`
  - `nnzero()`
  - `standardize()`
  - `norm()`  
- A custom `plot()` method for visualizing overlapping non-zero entries  
- Full documentation and examples on the package website (built with pkgdown)

## Development

This package was built for the UT Austin SDS 375 Data Product Development course and
includes:

- Test coverage using **testthat**
- Automated documentation using **roxygen2**
- A hosted website
- GitHub Actions CI (R CMD check)
